The zero--one laws of Kolmogorov and Hewitt--Savage in categorical probability

### 2019-12-06 categorical-zero-one.tex
cartesian monoidal cats and Problem 6.7

Strangely enough, the only example that we know of so far are monoidal posets, namely the finitary complete monoids of \Cref{poset_case}. For these, the causality axiom holds trivially since any two parallel morphisms are equal.

>>>>

Strangely enough, the only examples that we know of so far are of two kinds: first, cartesian monoidal categories (meaning that $\cC = \cC_\det$) with all products; and second, the finitary complete monoids of \Cref{poset_case} which are monoidal posets. For the former, the universal property of the monoidal structure implies that the causality axiom holds. For the latter, it holds trivially since any two parallel morphisms are equal.
